### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/conclusions.tex
Update

In this paper we argued that no feature selection methods have
previously targeted recall for the task of binary classification and
we proposed a model and objectives to address this task.  Empirically,
our results show that our high recall feature selection approach shows
strong performance on recall with significant improvements over other
methods in cases where there is a high feature to data ratio.
Future extensions of this work may examine tighter integration of the
feature selection method with the algorithm to make an \emph{embedded}
approach based on our model since at it's core is a voting-based
classifier.

>>>>

In this paper we argued that no feature selection methods have
previously targeted recall for the task of binary classification and
we proposed a model and objectives to address this task.  Empirically,
our results show that our high recall feature selection approach shows
strong performance on recall with significant improvements over other
methods in cases where there is a high feature to data ratio.
Future extensions of this work may examine tighter integration of the
feature selection method with the algorithm to make an \emph{embedded}
approach 
using the classifier implicit in our model.
%based on our model since at it's core is a voting-based
%classifier.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Update

\section{Empirical}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[tbp!]
\centering
\begin{tabular}{|l|r|r|r|r|l|} \hline
Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
\end{tabular}
\caption{\footnotesize Statistics of the various datasets evaluated in this work.}
\label{table:stats}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.}
\label{fig:perf_vs_dataset}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.}
\label{fig:perf_vs_classifier}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
\includegraphics[width=0.45\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
\caption{\footnotesize Performance distribution of various feature selection algorithms with samples taken for each dataset, classifier type, and stage of feature selection.}
\label{fig:perf_vs_fs_alg}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
novel feature selection algorithms DVE, DVL, CVE, CVL 
perform vs. classifier, noting that overall performance is best
for Naive Bayes followed by Logistic Regression and noticeably worse for
the SVM Linear --- it seems simply that the probabilistic nature of our feature selection
dovetail best with classification methods that are themselves probabilistic,
and overall best with Naive Bayes which makes the same independence assumptions.

Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms with
samples taken for each dataset, classifier type, and stage of feature
selection. This graph shows that our high recall feature selection improve recall with improvements noticeable when there is a high feature to data ratio such as in the Newsgroup(NG) and Spect(S) data sets.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[tbp!]
%\vspace{-1mm}
\centering
{\small 
\begin{tabular}{|l|r|r|r|r|l|} \hline
Dataset & \# Features & \# Data & \# Features/\# Data & \% True Labels & Feature Type\\ \hline \hline 
Breast Cancer(BC)	& 9	& 699	& 0.013	& 34 \%	& All Numeric\\ \hline
Diabetes(D)        & 8	& 768	& 0.010	& 35 \%	& All Numeric\\ \hline
Heart Statlog(HS)	& 13	& 270	& 0.048	& 44 \%	& All Numeric\\ \hline
Spect(S)	        & 22	& 80	& 0.275 & 33 \%	& Categorical\\ \hline
Vote(V)	        & 16	& 435	& 0.037	& 39 \%	& Categorical\\ \hline
Newsgroup(NG)	& 500	& 1963	& 0.255	& 49 \%	& All Binary\\ \hline
Horse Colic(HC)	& 22	& 368	& 0.060	& 37 \%	& Categorical (16) and numeric (6)\\ \hline
Credit-American(CR)	& 15	& 690	& 0.022	& 44 \%	& Categorical(9) and numeric (6)\\ \hline
Credit-German(GC)	& 20	& 1000	& 0.020 & 30 \%	& Categorical (13) and Numeric (7)\\ \hline
Hepatitis(H)	& 19	& 155	& 0.123	& 21 \%	& Categorical (13) and Numeric (6)\\ \hline
Ionosphere(I)	& 34	& 351	& 0.097	& 36 \%	& All Numeric\\ \hline
%KR-vs-KP	& 36	& 3196	& 0.011	& 48 \%	& All Categorical\\ \hline
%Labor	        & 16	& 57	& 0.281	& 35 \%	& Categorical (8) and Numeric (8)\\ \hline
%Mushroom	& 22	& 8124	& 0.003	& 48 \%	& All Categorical\\ \hline
%Sick	        & 29	& 3772	& 0.008	&  6 \%	& Categorical (23) and Numeric (6)\\ \hline
%Sonar	        & 60	& 208	& 0.288 & 47 \%	& All Numeric\\ \hline
\end{tabular}}
\vspace{-1mm}
\caption{\footnotesize Descriptive statistics of the various datasets evaluated in this work.}
\label{table:stats}
\vspace{-4mm}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Accuracy.pdf}\\
\includegraphics[width=0.85\textwidth]{./figures/dataset_perf/Recall.pdf}
\includegraphics[width=0.10\textwidth]{./figures/dataset_perf/legend.PNG}
\vspace{-2mm}
\caption{\footnotesize Performance of various feature selection algorithms per dataset, averaged across classifier type and each stage of feature selection.  Overall the newly proposed CVL method performs well on Recall on most datasets, while the Recall performance of other feature selection algorithms vary; interestingly the best performance is achieved for datasets a high ratio of features to data indicating that the strong conjunctive voting scheme of CVL may help reduce noise in feature selection for these datasets. }
\label{fig:perf_vs_dataset}
\vspace{-4mm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.42\textwidth]{./figures/class_perf/Accuracy.pdf}
\includegraphics[width=0.42\textwidth]{./figures/class_perf/Recall.pdf}
\includegraphics[width=0.15\textwidth]{./figures/class_perf/legend.PNG}
\vspace{-6mm}
\caption{\footnotesize Performance of various feature selection algorithms per classifier, averaged across dataset and each stage of feature selection.  DVE, DVL, CVE, and CVL align with the independence assumptions of Naive Bayes and the maximum (conditional) likelihood framework of Naive Bayes and Logistic Regression, which may explain the better excellent performance of these algorithms with these classifiers.}
\label{fig:perf_vs_classifier}
\end{figure*}
%\vspace{-6mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp!]
\centering
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall.pdf}
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall.pdf}\\
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall.pdf}
\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall.pdf}
%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectLogisticRegressionRecall2.pdf}
%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/SpectNaiveBayesRecall2.pdf}\\
%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupLogisticRegressionRecall2.pdf}
%\includegraphics[width=0.375\textwidth]{./figures/linegraphs/NewsgroupNaiveBayesRecall2.pdf}
\caption{\footnotesize Performance distribution of various feature selection algorithms for two datasets and classifier types at each stage of feature selection.  The conjunctive voting methods do best overall in these datasets.}
\label{fig:perf_vs_fs_alg}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Empirical Evaluation}

@@

@@

In Figure~\ref{fig:perf_vs_classifier}, we examine how well our 
novel feature selection algorithms DVE, DVL, CVE, CVL 
perform vs. classifier, noting that overall performance is best
for Naive Bayes followed by Logistic Regression and noticeably worse for
the SVM Linear --- it seems that the probabilistic nature of our feature selection
dovetail best with classifiers that are themselves probabilistic,
and overall best with Naive Bayes which makes the same independence assumptions.

Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms with
samples taken for each dataset, classifier type, and stage of feature
selection. This graph shows that our CVL high recall feature selection approach 
improves recall with the most improvement noticeable when there is a high
feature to data ratio such as in the Newsgroup (NG) and Spect (S) data
sets.  
%We conjecture the reason for this stems from the strong agreement of
%features provided by the conjunctive voting scheme that helps reduce noise
%during feature selection process.

### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex
Update

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. Wrapper methods, such as SVM-RFE \cite{guyon2002gene}, select features by evaluating their usefulness to a given classifier, they usually produce the best results but they are computationally expensive to large data sets or to high dimensional problems. Filter methods
evaluate feature subsets according to certain properties of features 
themselves. Within filter methods, feature selection algorithms can be
further classified into ranking methods and subset methods. The former
evaluate each feature independently, while the latter evaluate a
subset at a time \cite{brown2012conditional}. Listed below is a brief
introduction to popular feature selection algorithms that we later
compare to.

>>>>

Existing feature selection algorithms fall into categories of filter
methods and wrapper methods \cite{guyon_jmlr03}. Wrapper methods, such
as SVM-RFE \cite{guyon2002gene}, select features by evaluating their
usefulness \emph{after} training a given classifier; they often
produce good results but are computationally expensive when training
on large data sets or to high-dimensional problems.  In contrast,
filter methods evaluate feature subsets according to certain
properties of features themselves.  Within filter methods, feature
selection algorithms can be further classified into ranking methods
and subset methods. The former evaluate each feature independently,
while the latter evaluate a subset at a time
\cite{brown2012conditional}. Listed below is a brief introduction to
popular filter-based feature selection algorithms that we later
compare to.
